\documentclass[a4paper,10pt]{article}
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}

% Customizing hyperlink color
\hypersetup{colorlinks=true, urlcolor=blue}

\begin{document}

\begin{center}
    \textbf{\LARGE Rifaath XYZ} \\  % Change XYZ to your surname
    \small \href{mailto:your.email@example.com}{your.email@example.com} \textbullet{} +49 XXXX XXXXXX \textbullet{} \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile} \textbullet{} \href{https://github.com/yourgithub}{github.com/yourgithub}
\end{center}

\section*{Education}
\textbf{Master of Science, Artificial Intelligence} \hfill FAU Erlangen-Nürnberg \hfill 2023 -- Present \\
\textbf{Bachelor of Engineering, AI \& Machine Learning} \hfill University Name, India \hfill 2019 -- 2023 \\
GPA: 8.XX/10  % Replace with actual GPA

\section*{Experience}
\textbf{AI Automation Engineer Intern} \hfill Factweavers, India \hfill June 2023 -- Sept 2023
\begin{itemize}[leftmargin=*]
    \item Developed an AI-powered system for automating document workflows using LangChain and OpenAI.
    \item Implemented FAISS indexing to enhance content retrieval efficiency, reducing search latency by 30%.
    \item Built a query system supporting multiple LLMs, enabling seamless multi-document retrieval.
\end{itemize}

\textbf{Information Systems Audit Intern} \hfill Company Name, India \hfill Jan 2023 -- May 2023
\begin{itemize}[leftmargin=*]
    \item Conducted internal process audits and identified workflow inefficiencies across 10+ departments.
    \item Proposed automation strategies for financial operations, improving compliance monitoring.
\end{itemize}

\section*{Research \& Projects}
\textbf{Patent: Real-time Heartbeat Detection using Motion Magnification} \hfill \textit{Filed \& Published (2023)}
\begin{itemize}[leftmargin=*]
    \item Developed an algorithm that amplifies micro-movements in facial video footage to extract heart rate.
    \item Utilized Eulerian Video Magnification techniques, achieving 95\% accuracy compared to contact-based sensors.
\end{itemize}

\textbf{Multi-Document Query System} \hfill Personal Project
\begin{itemize}[leftmargin=*]
    \item Designed and implemented a scalable information retrieval system with RAG and LangChain.
    \item Integrated FAISS indexing for fast and efficient document similarity searches.
\end{itemize}

\section*{Skills}
\textbf{Programming}: Python, C++, Java, SQL \newline
\textbf{Frameworks}: PyTorch, TensorFlow, LangChain, OpenAI API \newline
\textbf{Tools}: Git, Docker, AWS, FAISS, Elasticsearch

\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item Digital Tech Fellow, FAU Erlangen (2025)
    \item AI for Business, Online Course (2024)
\end{itemize}

\end{document}
